Capsule Based Aspect Extraction

### 2020-05-29 paper/main.tex
added related work

\section{Related Work}
\label{sec:related}
In this section, you will describe in details the existing approaches to the problem you work on. For each approach, you need to provide a reference.

>>>>

\section{Related Work}
\label{sec:related}
The problem of aspect extraction has been well studied in the past decade. Initially, methods were mainly based on manually defined rules. \cite{HuLiu2004} proposed to extract different product features through finding frequent nouns and noun phrases. They also extracted opinion terms by finding the synonyms and antonyms of opinion seed words through WordNet. Following this, a number of methods have been proposed based on freequent item mining and dependency information to extract product aspects \cite{Zhuang2006} \cite{Somasundarn2009} \cite{Qiu2011}. These models heavily depend on predefined rules which work well only when the aspect terms are restricted to a small group of nouns. Supervised learning approaches generally model aspect extraction as a standard sequence labeling problem. \cite{Jin2009} \cite{Li2010} proposed to use hidden Markov models(HMM) and conditional random fields(CRF) respectively with a set of manually-extracted features. More recently, different neural models \cite{Yin2016} \cite{Wang2016} were proposed to automatically learn features for CRF-based aspect extraction. Rule-based models are usually not refined enough to categorize the extracted aspect terms. On the other hand, supervised learning requires large amounts of labeled data for training purposes.

Unsupervised approaches, especially topic models, have been proposed subsequently to avoid reliance on labeled data. Generally, the outputs of those models are word distributions or rankings for each aspect. Aspects are naturally obtained without separately performing extraction and categorization. Most existing works \cite{Brody2010UAS} \cite{Zhao2010JMA} \cite{Mukherjee2012} \cite{Chen2014} are based on variants and extensions of LDA \cite{Blei2003}. Recently, \cite{Wang2015} relies on a substantial amount of prior knowledge such as part-of-speech(POS) tagging and sentiment lexicons. A biterm topic models (BTM) that generates co-occurring word pairs was proposed in \cite{Yan2013}.

Attention models \cite{Mnih2014} have recently gained popularity in training neural networks and have been applied to various natural language processing tasks, including machine translation \cite{Bahdanau2015NMT}, sentence summarization \cite{Rush2015}, sentiment classification
